
I would like to thank my DPhil supervisor, Roxanne Guenette, for her constant support. She has been a wonderful supervisor from whom I have learned a lot. I would like to thank her in particular for all the opportunities she has given me, for being extremely approachable and for her kindness: she sets the standard of what a supervisor should be.
Thank you to my co-supervisor, Giles Barr, who has always been available to support me.\\

I certainly would not have been able to complete this work without the advice and support of Anne Schukraft. She is an incredible scientist and she represents all the good things I love about Fermilab. A special thanks also goes to Sam Zeller, for all her invaluable feedback and for always being available to help.\\ 

I am honoured to have been part of Oxford Physics and would like to thank all the people I interacted with in past years, especially the Oxford neutrino group I worked with: Roberto Soleti, Wouter Van De Pontseele and Matt Bass. \\

I have been very fortunate to work at Fermilab for part of my DPhil, and would like to thank who on MicroBooNE helped me throughout my time on the experiment, especially Corey Adams and Kazu Terao. I learned so much from them.
Thank you also to Colton Hill and Adam Lister, for being part of this journey and for all the lovely moments spent together at Fermilab. \\

I would also like to thank my parents. I owe so much to them for their constant support throughout my DPhil and my entire life.  
Finally, my biggest thank you goes to who has been standing by my side during the past years. Thank you Cecilia. There is no way I could have managed this without you.