This thesis and the work presented in it are my own and were produced by me as a result of my own original research. Results and figures from published works by others have been clearly attributed, and this work has not been submitted for another qualification at this or any other university.

After a brief introduction in Chapter~\ref{ch:introduction}, Chapters~\ref{ch:neutrino_physics} and~\ref{ch:neutrino_interactions} give some background information about the theory motivating the work presented in this thesis, and Chapter~\ref{ch:microboone} describes the MicroBooNE experiment whose data was analysed in this work.  These chapters represent my summary of the work of others, and all relevant papers and documents have been cited. However, some elements of the interpretations of how neutrino interactions affect oscillation analysis and on the importance of neutrino interaction measurements (Sections~\ref{sec:neutrino_oscillations_challenges} and~\ref{sec:remarks}) are my own.

Chapter~\ref{ch:reconstruction} discusses the event reconstruction used for the analysis in this thesis. The algorithms that lead to track/shower reconstruction, the muon momentum measurement and part of the optical reconstruction and flash matching were developed by others, and the relevant technical reports have been referenced. My contributions to the work presented in this chapter are all the cosmic ray tagging algorithms that make use of the detector geometry and optical information, as well as those that identify cosmic ray tracks piercing the sides of the detector and cosmic ray muons that enter and stop in the detector. Moreover, considerable parts of the optical reconstruction and flash matching were developed by me.

The event selection performed to select muon neutrino candidate events detailed in Chapter~\ref{ch:event_selection} is all my own work. The measurements of the total, single- and double-differential muon-neutrino charged-current inclusive cross-sections described in Chapter~\ref{ch:extraction} were all done by me. The implementation, study and propagation of all the systematic uncertainties that affect the measurement, described Chapter~\ref{ch:systematics}, are all my original work. The entire analysis framework used for this analysis was developed by me.

The results, as well as the hypothesis testing between two different theoretical models in Chapter~\ref{ch:cross_section_results}, the interpretations presented in Chapter~\ref{ch:conclusions}, as well as all the appendices, are all my own work.